Summary Tables

### 2019-05-02 summary_tables.Rmd
Transpose trip data frames

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% dplyr::filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- nrow(df1)
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() /  u_trips * 100, round_to)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td[2:6, 1] <- rownames(scen_prop)
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

>>>>

for(city in cities){

  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% dplyr::filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- nrow(df1)
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() /  u_trips * 100, round_to)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td[2:6, 1] <- rownames(scen_prop)
  td <- as.data.frame(t(td))
  print(kable(t(td), caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}
